Baseline centering problem

### 2018-12-13 paper/tangotd.tex

\newcommand{\Dir}{\mathcal{D}}

@@

>>>>

\newcommand{\Dir}{\mathcal{D}}
\newcommand{\green}{\mathcal{G}}

@@

\paragraph{A learned representation for $\Delta^{-1}$.} $\Delta^{-1}$
contains all the necessary to do policy gradient or actor-critic with
arbitrary reward functions, as seen above. It is feasible to store a
compact and useful representation of $\Delta^{-1}$? Ideally, such a
representation should be learned from the \emph{two-sided} Bellman
equations
\begin{equation}
\Delta^{-1}=\Id + P \Delta^{-1},\qquad \Delta^{-1}=\Id + \Delta^{-1}P
\end{equation}
which represent that, when observing a transition $s\to s'$, we update
both the ways to arrive at $s'$ and the ways to start at $s$.

``Universal value function approximators'' do a bit of that, but only
with the left (ordinary) Bellman equation.

We propose to learn two functions $\green(s)$ and $f(s)$ from states into
a state representation $E$, such that for any test function $\psi\from
S\to \R$, for any $s_1\in S$,
\begin{equation}
\E_{s_2\sim \rho}\,\green(s_1)\cdot
f(s_2)\psi(s_2)\approx \transp{\1_{s_1}}\,\Delta^{-1} \psi
\end{equation}

If the state space is finite and if we use a one-hot representation, a
solution is indeed $E=\R^{\#S}$ with
\begin{equation}
f(s_2)=\1_{s_2},\qquad
(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}/\rho(s_2)
\end{equation}

The reason for this form is the following: $E$ is supposed to represent
distributions/functions over states. $f(s_2)$ is supposed to be
mapped to $\1_{s_2}$. $\green(s_1)$ is supposed to be mapped to the
density wrt $\rho$ of the fundamental matrix at $s_1$ (the occupation
distribution from $s_1$: $\transp{\1_{s_1}}\sum_t P^t$, where as usual I
omit constants\footnote{To deal with constants, we probably have to be
able to predict \emph{differences} $\psi(s_2)-\psi(s_2')$.}). In
particular, $\E_{s_2\sim \rho}f(s_2)\psi(s_2)$ is supposed to represent
the vector with components $\rho \psi(s_2)$. Then the scalar product in
$E$ represents integration/summation with respect to $\rho$.
